Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling

### 2021-02-02 papers/intro_paper/results_lvc.tex
added reference to SNRs in GWTC-2 TGR

The LIGO-Virgo Collaboration recently released their testing GR
catalogue containing results for events observed
during O3a~\cite{Abbott:2020jks}. For the test that we here present, the results shown in~\cite{Abbott:2020jks} only include events which pass a threshold for the median redshifted total mass $\geq 90 \Mo$ and SNRs in the pre- and
post-merger regions $\geq 8$\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.}. 
%
The SNR threshold ensures that the signal contains sufficient information in both the inspiral and merger stages to break the degeneracy between the binary's total mass and the non-GR deviations $(\df{220}, \dtau{220})$. Such strong degeneracy is present for low-SNR events with negligible higher-modes and for which only the post-merger is detectable rendering the measurement of $(\df{220}, \dtau{220})$ impossible for those cases.\rb{should we show an example where this degeneracy happens in the appendix? We can show a corner plot with $(\df{220}, \dtau{220}, M_{\rm total })$ for 21g in the appendix for example. And perhaps also for GW150914 for comparison.}\abhi{I would be fine with this. Perhaps we should have a discussion about how best to put it in the appendix, if we decide to.}
On the other hand the total mass threshold $\geq 90 \Mo$ was employed due to the fact that this analysis is computationally expensive, and also because we expected these events to be the most promising for ringdown studies. However, since the SNR threshold alone should be sufficient for the analysis, for this paper we run the test on all the events listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and post-merger regions $\geq 8$, without imposing any mass threshold.

>>>>

The LIGO-Virgo Collaboration recently released their testing GR
catalogue containing results for events observed
during O3a~\cite{Abbott:2020jks}. For the test that we here present, the results shown in~\cite{Abbott:2020jks} only include events which pass a threshold for the median redshifted total mass $\geq 90 \Mo$ and SNRs in the pre- and
post-merger regions $\geq 8$\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis. The SNR values are listed in Table 4 of \cite{Abbott:2020jks}}. 
%
The SNR threshold ensures that the signal contains sufficient information in both the inspiral and merger stages to break the degeneracy between the binary's total mass and the non-GR deviations $(\df{220}, \dtau{220})$. Such strong degeneracy is present for low-SNR events with negligible higher-modes and for which only the post-merger is detectable rendering the measurement of $(\df{220}, \dtau{220})$ impossible for those cases.\rb{should we show an example where this degeneracy happens in the appendix? We can show a corner plot with $(\df{220}, \dtau{220}, M_{\rm total })$ for 21g in the appendix for example. And perhaps also for GW150914 for comparison.}\abhi{I would be fine with this. Perhaps we should have a discussion about how best to put it in the appendix, if we decide to.}
On the other hand the total mass threshold $\geq 90 \Mo$ was employed due to the fact that this analysis is computationally expensive, and also because we expected these events to be the most promising for ringdown studies. However, since the SNR threshold alone should be sufficient for the analysis, for this paper we run the test on all the events listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and post-merger regions $\geq 8$, without imposing any mass threshold.
